Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-14 ms.tex
starting to edit/re-write MCMC sampling description/discussion

The following subsections detail our procedure for constraining the 
two-component dust emission model parameters which are permitted to vary
spatially. We perform two types of fits: (1) full-resolution 
$6.1'$ fits, in which just two parameters, the SED normalization and the hot 
dust temperature $T_2$, vary spatially and (2) lower-resolution fits in which 
$f_1$ is also allowed to vary from one line of sight to another.

@@

\subsection{Pixelization}
\label{sec:pix}
For the purpose of fitting, we break the sky into $\sim$50 million pixels of 
angular size $\sim$1.72$'$, defined by the HEALPix pixelization in Galactic 
coordinates, with $N_{side}$=2048. This pixelization is convenient because it 
is the same format in which the \PLANCK~HFI maps were released, and because it 
adequately samples the $6.1'$ FWHM maps under consideration in our 
full-resolution fits. Our procedure will fit the intensity measurements in each
spatial pixel independently.

\subsection{Sampling Parameters}
\label{sec:samp}
As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
 fixed, while the dust spectrum normalization and dust temperature vary for
each line-of-sight. In order to predict the dust SED for a given pixel, we are 
therefore left with two remaining degrees of freedom, and must choose an 
appropriate set of two parameters to sample and thereby constrain via MCMC. To 
determine the SED normalization in each pixel, we draw samples in 
$\tilde{I}_{545}$, the broadband intensity in the 545 GHz bandpass, as defined 
in Equation \ref{eqn:inten}. With the four aforementioned global parameters 
fixed, the dust spectrum shape is determined entirely by the two dust 
temperatures, which are coupled. To constrain the dust temperatures,
 we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
compute the corresponding value of $T_1$, thereby specifying ($\beta$, $T$) for
both MBB components and thus fully specifying the SED shape. In principle,
we could sample in either $T_1$ or $T_2$, but have chosen to sample in $T_2$ 
because emission from this component dominates in the relatively high frequency
bands which most strongly constrain the dust temperatures.

@@

Here \{$I$\} denotes the set of observed broadband intensities, $I_{217}$, 
$I_{353}$, etc. The likelihood function is given by:

@@

In order to obtain reasonable fitting results at high latitude where the data 
is noisy, we include the prior on $T_2$:

%what about the offset uncertainty for 217 GHz

@@

% maybe have a section justifying the T2 prior value of 16.2K, presumably using
% FIRAS as a cross-check?

With $\bar{T}_2$ = 16.2 K and $\sigma_{\bar{T}_2}$ = 1.4 K. In principle, there
can also be an informative prior on $\tilde{I}_{545}$. However, we have chosen 
to assume a uniform prior on the SED normalization and, as a matter of 
notation, will omit $P(\tilde{I}_{545})$ henceforward. In practice we always 
perform computations using logarithms of the relevant probabilities.
%mention something about the proposal distribution at some point?

@@

\begin{figure*}
\begin{center}
\epsfig{file=compare_lofreq.eps, width=6.6in}
\caption{\label{fig:lofreq} Comparison of low-frequency thermal dust emission 
predictions.}
\end{center}
\end{figure*}

>>>>

The following subsections detail our procedure for constraining the 
two-component dust emission model parameters which are permitted to vary
spatially. We use the MCMC procedure described to perform two types of fits: 
(1) full-resolution $6.1'$ fits, in which only  the SED normalization and dust 
temperatures vary spatially, and (2) lower-resolution fits in which $f_1$ is 
also allowed to vary from one line of sight to another.

@@

\subsection{Pixelization}
\label{sec:pix}
For the purpose of fitting, we divide the sky into $\sim$50 million pixels of 
angular size $\sim$1.72$'$, defined by the HEALPix pixelization in Galactic 
coordinates, with $N_{side}$=2048. This pixelization is convenient because it 
is the same format in which the \PLANCK~HFI maps were released, and because it 
adequately samples the $6.1'$ FWHM maps under consideration in our 
full-resolution fits. Our procedure will fit the intensity measurements in each
spatial pixel independently.

\subsection{Sampling Parameters}
\label{sec:samp}
As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
fixed, while the dust spectrum normalization and dust temperatures are allowed 
to vary for each line-of-sight. In order to predict the dust SED for a given 
pixel, we are thus left with two remaining degrees of freedom, and must 
choose an appropriate set of two parameters to sample and thereby constrain via
MCMC. To determine the SED normalization in each pixel, we draw samples in 
$\tilde{I}_{545}$, the `IRAS convention' intensity in the 545 GHz bandpass, 
as defined in Equation \ref{eqn:inten}. With the four aforementioned global 
parameters fixed, the dust spectrum shape is determined entirely by the two 
dust temperatures, which are coupled. To constrain the dust temperatures,
 we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
compute the corresponding value of $T_1$, thereby determining the temperature
and emissivity power law index for both MBB components and thus fully 
specifying the SED shape. In principle, we could sample in either $T_1$ or 
$T_2$, but have chosen to sample in $T_2$ because emission from this component 
dominates in the relatively high frequency bands which most strongly constrain 
the dust temperatures.

@@

Here \{$I$\} denotes the set of observed intensities quoted under
the `IRAS convention': $I_{217}$, $I_{353}$, ... The likelihood function is 
given by:

@@

In order to ensure reasonable fit results at high latitude where the intensity 
constraints are noisy, we include a prior on $T_2$:

@@

% justification for T2 prior standard deviation
With $\bar{T}_2$ = 15.7 K and $\sigma_{\bar{T}_2}$ = 1.4 K. The $T_2$ prior 
mean is chosen based on the typical high-latitude $T_2$ value derived from
the correlation slope analysis from $\S$\ref{sec:global}. In principle, there 
can also be an informative prior on $\tilde{I}_{545}$. However, we have chosen 
to assume a uniform prior on the SED normalization and, as a matter of 
notation, will omit $P(\tilde{I}_{545})$ henceforward. In practice we always 
perform computations using logarithms of the relevant probabilities.
%mention something about the proposal distribution at some point?

@@

\begin{figure*}
\begin{center}
\epsfig{file=compare_lofreq.eps, width=6.8in}
\caption{\label{fig:lofreq} Comparison of low-frequency thermal dust emission 
predictions.}
\end{center}
\end{figure*}
